---
title: "**Multi100 Project**"
author: "Theiss Bendixen^[Aarhus University, Denmark. Contact: tb@cas.au.dk]"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
   - \usepackage{float} # keeps figures and tables in place
numbersections: true
bibliography: [multi100-bib.bib, grateful-refs.bib]
---

```{r lockfile, include=FALSE}
# to initialize and embed the package environment - generates the call renv::use(...) below
# renv::embed()

renv::use(
  "BH@1.78.0-0",
  "Brobdingnag@1.2-7",
  "DT@0.20",
  "HDInterval@0.2.2",
  "MASS@7.3-54",
  "Matrix@1.3-4",
  "Pakillo/grateful@HEAD",
  "R6@2.5.1",
  "RColorBrewer@1.1-2",
  "Rcpp@1.0.8",
  "RcppEigen@0.3.3.9.1",
  "RcppParallel@5.1.5",
  "StanHeaders@2.21.0-7",
  "abind@1.4-5",
  "arrayhelpers@1.1-0",
  "askpass@1.1",
  "backports@1.4.1",
  "base64enc@0.1-3",
  "bayesplot@1.8.1",
  "bit64@4.0.5",
  "bit@4.0.4",
  "bridgesampling@1.1-2",
  "brms@2.17.0",
  "broom@0.7.12",
  "bslib@0.3.1",
  "cachem@1.0.6",
  "callr@3.7.0",
  "checkmate@2.0.0",
  "cli@3.2.0",
  "clipr@0.8.0",
  "coda@0.19-4",
  "codetools@0.2-18",
  "colorspace@2.0-3",
  "colourpicker@1.1.1",
  "commonmark@1.7",
  "cpp11@0.4.2",
  "crayon@1.5.0",
  "crosstalk@1.2.0",
  "curl@4.3.2",
  "desc@1.4.0",
  "digest@0.6.29",
  "distributional@0.3.0",
  "dplyr@1.0.8",
  "dygraphs@1.1.1.6",
  "ellipsis@0.3.2",
  "evaluate@0.15",
  "fansi@1.0.2",
  "farver@2.1.0",
  "fastmap@1.1.0",
  "fontawesome@0.2.2",
  "forcats@0.5.1",
  "fs@1.5.2",
  "future@1.24.0",
  "generics@0.1.2",
  "ggdist@3.1.1",
  "ggplot2@3.3.5",
  "ggridges@0.5.3",
  "globals@0.14.0",
  "glue@1.6.1",
  "gridExtra@2.3",
  "gtable@0.3.0",
  "gtools@3.9.2",
  "haven@2.4.3",
  "highr@0.9",
  "hms@1.1.1",
  "htmltools@0.5.2",
  "htmlwidgets@1.5.4",
  "httpuv@1.6.5",
  "igraph@1.2.11",
  "inline@0.3.19",
  "isoband@0.2.5",
  "jquerylib@0.1.4",
  "jsonlite@1.8.0",
  "knitr@1.39",
  "labeling@0.4.2",
  "later@1.3.0",
  "lattice@0.20-45",
  "lazyeval@0.2.2",
  "lifecycle@1.0.1",
  "listenv@0.8.0",
  "loo@2.4.1",
  "magrittr@2.0.2",
  "markdown@1.1",
  "matrixStats@0.61.0",
  "mgcv@1.8-38",
  "mime@0.12",
  "miniUI@0.1.1.1",
  "modelr@0.1.8",
  "munsell@0.5.0",
  "mvtnorm@1.1-3",
  "nleqslv@3.3.2",
  "nlme@3.1-153",
  "numDeriv@2016.8-1.1",
  "openssl@1.4.6",
  "packrat@0.7.0",
  "parallelly@1.30.0",
  "pillar@1.7.0",
  "pkgbuild@1.3.1",
  "pkgconfig@2.0.3",
  "plyr@1.8.6",
  "posterior@1.2.0",
  "prettyunits@1.1.1",
  "processx@3.5.2",
  "progress@1.2.2",
  "promises@1.2.0.1",
  "ps@1.6.0",
  "purrr@0.3.4",
  "rappdirs@0.3.3",
  "readr@2.1.2",
  "remotes@2.4.2",
  "renv@0.15.4",
  "reshape2@1.4.4",
  "rlang@1.0.1",
  "rmarkdown@2.14",
  "rprojroot@2.0.2",
  "rsconnect@0.8.25",
  "rstan@2.21.3",
  "rstantools@2.1.1",
  "rstudioapi@0.13",
  "sass@0.4.1",
  "scales@1.1.1",
  "shiny@1.7.1",
  "shinyjs@2.1.0",
  "shinystan@2.5.0",
  "shinythemes@1.2.0",
  "sourcetools@0.1.7",
  "stringi@1.7.6",
  "stringr@1.4.0",
  "svUnit@1.0.6",
  "sys@3.4",
  "tensorA@0.36.2",
  "threejs@0.3.3",
  "tibble@3.1.6",
  "tidybayes@3.0.2",
  "tidyr@1.2.0",
  "tidyselect@1.1.2",
  "tinytex@0.38",
  "tzdb@0.2.0",
  "utf8@1.2.2",
  "vctrs@0.3.8",
  "viridisLite@0.4.0",
  "vroom@1.5.7",
  "withr@2.4.3",
  "xfun@0.29",
  "xtable@1.8-4",
  "xts@0.12.1",
  "yaml@2.3.5",
  "zoo@1.8-9"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, include=FALSE, warning=FALSE)
```

# Introduction
This document reports on a contribution (ID: YMESM) to the **Multi100 Project** of the Center for Open Science. The re-analysis concerns the following paper:

Cohen, J., Dupas, P., & Schaner, S. (2015). Price subsidies, diagnostic tests, and targeting of malaria treatment: evidence from a randomized controlled trial. *American Economic Review*, *105*(2), 609-45.

The study was a randomized controlled trial on the effect of price subsidies on access and uptake of a particular malaria treatment, artemisinin combination therapies (ACTs), between households. The focal claim to be assessed is: *'... a very high subsidy ... increases access [to antimalarials]'* (p. 609.). In this document, I first spell out the statistical approach of my re-analysis (Section \ref{stat}), report key results (Section \ref{results}), and a brief conclusion (Section \ref{conclusion}). Finally, I report supplementary plots (Section \ref{supps}) and all `R` [@base, version 4.1.2] packages and dependencies used (Section \ref{pkgs}).

# Statistical model {#stat}
Since the outcome -- self-reported treatment of an illness episode with an ACT -- is binary (either an ACT was used or it wasn't), we model the data with an aggregated binomial likelihood. That is, each row in the data set is a household. We fit two Bayesian multilevel regression models that are identical except that one collapses the ACT subsidies into a single variable and the other treats the subsidy levels as separate. We refer to the first model as `pAfit` and the second as `pBfit`, based on Table 2, Panel A and B, of the original study. We subset the data similarly to the original study, such that we 1) only focus on the first illness episode reported by each household subsequent to voucher distribution and 2) exclude households that were also provided with a subsidy for rapid diagnostic malaria tests (p. 627). Our choice of covariates is likewise fully informed by the original study.

In formal notation, our models take the following form, including prior distributions^[Note that we use a 'centered' multilevel parameterization in notation, but `brms` by default employ a 'non-centered' variant for computational efficiency.]:
\begin{align}
	y_i &\sim \textrm{Binomial}( n_i , p_i )\\
	\textrm{logit}(p_i) &= \alpha_{\textsc{stratum}[i]} + \beta_{\textsc{stratum}[i]}A_i + \gamma H_i\\
	H_i &\sim \textrm{Normal}(\nu, \sigma_H)\\
	\nu &\sim \textrm{Normal}(0, 1)\\
	\sigma_H &\sim \textrm{Exponential}(1)\\
	\alpha &\sim \textrm{Normal}(0, 1.5 )\\
	\beta &\sim \textrm{Normal}(0, 1)\\
	\gamma &\sim \textrm{Normal}(0, 1)
\end{align}

where $y$ is the binary outcome, and $p$ is the probability of taking an ACT for the *i*th household (line 1). Since some households reported more than one illness episodes, we allow the number of illness episode $n$ (i.e., the number 'trials' in the binomial model) to vary by household, denoted by subscript $i$. In the multilevel linear model (line 2), each randomization stratum gets its own varying intercept $\alpha_{\textsc{stratum}}$ and varying slopes for subsidy level $\beta_{\textsc{stratum}}$. We also include age of household head as a fixed effect $\gamma$, while we (line 3) impute missing values in household head age $H$ with draws from a Normal distribution with mean $\nu$ and standard deviation $\sigma_H$ estimated from the sample, which are themselves given weakly regularizing priors (line 4-5). The prior for the average intercept $\alpha$ and for the average slope of subsidy level $\beta$ are both given weakly regularizing priors (line 6-7), as are the fixed effect of household head age, which is standardized and hence centered on zero (line 8).

The varying effects for randomization strata ensure *partial pooling* across strata, such that each stratum is simultaneously and proportionally *informing* and *informed by* the average intercept and slope estimates [cf., @mcelreath_statistical_2020]. This reduces the risk of over-fitting and improves computational efficiency. Partial pooling is facilitated via a variance-covariance matrix with multivariate Gaussian priors, where $\mathbf{S}$ is a diagonal matrix of intercept $\alpha$ and slope $\beta$, and $\mathbf{R}$ is their correlation matrix with a prior distribution of LKJcorr(4) [@lewandowski2009generating]. The standard deviations among intercepts $\sigma_\alpha$ and slopes $\sigma_\beta$ are both given an Exponential(1) prior.
\begin{align*}
\begin{bmatrix} \alpha_{\textsc{stratum}}\\ \beta_{\textsc{stratum}}\end{bmatrix} &\sim \textrm{Multivariate Normal}\left({\begin{bmatrix}\alpha\\ \beta\end{bmatrix}}, \mathbf{S}\right)\\
\mathbf{S} &= \left(\begin{matrix} \sigma_\alpha & 0 \\ 0 & \sigma_\beta \end{matrix}\right) \mathbf{R} \left(\begin{matrix} \sigma_\alpha & 0 \\ 0 & \sigma_\beta \end{matrix}\right)
\end{align*}

Analyses are conducted with the `brms` package [@burkner_brms_2017; @burkner_advanced_2018; @brmsirt], an interface to the probabilistic programming language `Stan` [@stan:2017; @stan_2020]. MCMC diagnostics and posterior predictive checks were reasonable. Data wrangling and plotting are primarily facilitated by the `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], and `tidybayes` [@tidybayes] packages[^pkgs]. The report is written in `R Markdown` [@rmarkdown_package; @rmarkdown_guide].

[^pkgs]: The package `renv` [@renv] ensures a reproducible package environment. See Section \ref{pkgs} for a list of `R` packages, their dependencies, and version number used for this project, created using `grateful` [@grateful].

```{r load}
# load packages
library(grateful) # for package citations
library(tidyr) # for data wrangling
library(dplyr) # for data wrangling
library(haven) # for loading .dta file
library(brms) # for Bayesian multilevel modeling
library(ggplot2) # for plotting
library(tidybayes) # predictions and plotting

# increase memory
memory.limit(size=56000)

# seed for reproducibility
set.seed(2022)

# load original data
dta <- read_dta("ACT_IllLvlMainWithMalProbs_FINAL_pub.dta") |> as.data.frame()

# filter data set, as the original study did -- re-use name from original analysis script
all_ill_prob <- subset(dta, first_ep==1 & ex_post==0 & rdt_any==0)

```

```{r wrangling}
# collaps all ACT subsidy types
all_ill_prob$act_any <- ifelse(all_ill_prob$act40==1 | 
                                 all_ill_prob$act60==1 | 
                                 all_ill_prob$act100==1, 
                               1, 0) |> as.integer()

# replace sample-mean imputed values with NAs to allow Bayesian imputation, and then standardize 
all_ill_prob$B_head_age_bimps <- with(all_ill_prob, 
                                      ifelse(B_head_age_missing==1, NA, B_head_age_imputed)) |> scale()

# subset to relevant variables
aggrvars <- c("householdid", "took_act","coartemprice","act40","act60", "act100","act_any", "totstrata", "B_head_age_bimps")
all_ill_prob_sub <- all_ill_prob[aggrvars]

# only complete cases for the outcome (will be dropped either way by brm() below)
all_ill_prob_sub <- all_ill_prob_sub[complete.cases(all_ill_prob_sub$took_act),]

# compute trials (number of illness episodes) per household and aggregate
all_ill_prob_aggr <- all_ill_prob_sub |> 
  group_by(householdid) |> 
  mutate(trials = n()) |>
  group_by(householdid, 
           coartemprice, 
           act40, act60, act100, 
           act_any, 
           totstrata,
           B_head_age_bimps, 
           trials) |>
  summarize(took_act = sum(took_act)) |>
  ungroup()|> as.data.frame()

# check that NAs in age were retained (should be 29)
sum(is.na(all_ill_prob_aggr$B_head_age_bimps))

# check that number of trials matches number of obs. in original study (should be 631, see Table 2)
sum(all_ill_prob_aggr$trials)

# treat subsidy intervention as factor and set no subsidy ("coartemprice==500") as reference
all_ill_prob_aggr$coartemprice <- factor(all_ill_prob_aggr$coartemprice, levels = c("500","40", "60", "100"))
```

```{r pAmodel, dependson=c("wrangling")}
iter <- 2000 # set iterations
chains <- 4 # set number of chains

priors <- set_prior("normal(0, 1.5)", class = "Intercept", resp = "tookact") +
          set_prior("normal(0, 1)", class = "Intercept", resp = "Bheadagebimps") +
          set_prior("normal(0, 1)", class = "b", coef="miB_head_age_bimps", resp = "tookact") +
          set_prior("exponential(1)", class = "sd", resp = "tookact") +
          set_prior("exponential(1)", class = "sigma", resp = "Bheadagebimps") +
          set_prior("lkj_corr_cholesky(4)", class = "cor")

# set priors
pApriors <- priors + set_prior("normal(0, 1)", class = "b", coef = c("act_any"), resp = "tookact")

# binomial aggregate model with household-varying trials, pooled subsidy levels (Table 2, Panel A)
# and Bayesian imputation of missing age values
pAformula <- bf(took_act | trials(trials) ~ act_any + (act_any | totstrata) + mi(B_head_age_bimps),
                     family = binomial()) +
  bf(B_head_age_bimps | mi() ~ 1,
     family = gaussian()) + set_rescor(FALSE)

# fit model
pAfit <- brm(pAformula,
                  data = all_ill_prob_aggr, 
                  prior = pApriors,
                  chains = chains, cores = 4, iter = iter,
                  seed = 2021, control = list(adapt_delta=0.99))

```

```{r pBmodel, dependson=c("wrangling","pAmodel")}
# set priors
pBpriors <- priors + set_prior("normal(0, 1)", 
                               class = "b", 
                               coef = c("coartemprice40","coartemprice60","coartemprice100"), 
                               resp = "tookact")

# binomial aggregate model with household-varying trials, for each subsidy level (Table 2, Panel B)
# and Bayesian imputation of missing age values
pBformula <- bf(took_act | trials(trials) ~ coartemprice  + (coartemprice | totstrata) + mi(B_head_age_bimps),
                     family = binomial()) +
  bf(B_head_age_bimps | mi() ~ 1,
     family = gaussian()) + set_rescor(FALSE)

# fit model
pBfit <- brm(pBformula,
                  data = all_ill_prob_aggr, 
                  prior = pBpriors,
                  chains = chains, cores = 4, iter = iter,
                  seed = 2021, control = list(adapt_delta=0.99))

```

```{r model-diagnosis}
# model diagnostics
rstan::check_hmc_diagnostics(pAfit$fit)
rstan::check_hmc_diagnostics(pBfit$fit)

# convenient posterior predictive check for ACT outcome
pp_check(pAfit, type = "bars", resp = "tookact", ndraws = 50)
pp_check(pBfit, type = "bars", resp = "tookact", ndraws = 50)

# convenient posterior predictive check for imputed age
pp_check(pAfit, resp = "Bheadagebimps", ndraws = 50)
pp_check(pBfit, resp = "Bheadagebimps", ndraws = 50)
```

```{r pAplot-prep}
# Panel A: Contrast plot prep

# simulate counterfactual population: leave covariates as observed but toggle intervention on/off ofr all households
pA_pred <-  with(all_ill_prob_aggr,
             data.frame(
               householdid = rep(householdid,2),
               act_any = c(rep(0, length(householdid)), rep(1, length(householdid))),
               B_head_age_bimps = rep(B_head_age_bimps,2),
               trials = rep(trials,2),
               totstrata = rep(totstrata,2)))

# plug posterior mean of imputations for missing age into prediction grid
age_impute <- rstan::extract(pAfit$fit,"Ymi_Bheadagebimps")$"Ymi_Bheadagebimps"
age_impute_mean <- apply(age_impute, 2, mean)
age_impute_idx <- which(is.na(pA_pred$B_head_age_bimps))
pA_pred[age_impute_idx,]$B_head_age_bimps <- age_impute_mean

# push posterior draws through prediction grid and calculate contrast
pA_marginal <- pA_pred |>
  tidybayes::add_epred_draws(pAfit, 
                             re_formula = NULL, # include all random effects
                             resp = "tookact",
                             robust = FALSE) |> # posterior mean (FALSE) or median? 
  group_by(householdid, .draw) |>
  # get the percentage increase btw. subsidy (any subsidy level) vs. no subsidy
  mutate(contrast = ((.epred[act_any==1]-.epred[act_any==0])/.epred[act_any==0])*100) |> 
  ungroup()

```

# Results {#results}
Here, we report results. Our target quantity of interest is *the contrast in posterior predicted probabilities of taking an ACT between the price subsidy interventions compared to no subsidy*. This contrast is akin to an average treatment effect and we compute it (in percentage) as 
$$\dfrac{\mathbb{E}(Y=1|\mathrm{Subsidy}=1) - \mathbb{E}(Y=1|{\mathrm{Subsidy}}=0)}{\mathbb{E}(Y=1|\mathrm{Subsidy}=0)}\times 100$$ for each draw of the posterior distribution (in this case, `r nrow(pA_marginal)/nrow(pA_pred)` post-warmup draws), which we then in turn summarize by its mode and 95% highest posterior density interval (HPDI; i.e., the smallest possible interval containing 95% of the parameter estimates). A positive contrast thus means that the subsidies increase the likelihood of taking an ACT. Further, the contrast marginalizes over the distribution of age as well as the randomization strata by simulating a counter-factual population, wherein all households were assigned to both the treatment and the control group while retaining covariates as observed^[For the households with missing values in age of household head, we get predictions for the posterior mean of the imputed values.]. This procedure is often referred to as *g-computation* or *standardisation*.

## Any subsidy level & across subsidy levels
Figure \ref{pAplot} shows the computed contrast as a posterior predicted density for any amount of subsidy (`pAfit` model). Zero (the dotted line) represents equal chance of taking an ACT between the two groups.

```{r pAplot, include = TRUE, dependson = "pAplot-prep", message=FALSE, fig.width=4.5, fig.height=3, fig.cap = "\\label{pAplot} Results from \\texttt{pAfit} model. Contrast in predicted probabilities of taking an ACT between the price subsidy intervention (any of the subsidy levels) compared to no subsidy. Zero (the dotted line) represents equal chance of taking an ACT between the two groups. The density is normalized and the gradient reflects posterior mass. The point represents the mode of the distribution with a 95% HPDI."}
# Panel A contrast plot
ggplot(pA_marginal, aes(x = contrast)) +

  stat_halfeye(aes(fill = stat(x > 0), slab_alpha = stat(f)), 
               normalize="all",
               .width = 0.95,
               size = 1,
               point_interval = "mode_hdci", # summarize the distribution with its mode and HPDI
               show.legend=FALSE,
               n = 2000) +
  
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("black", "#3182BD")) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha= 0.5) +
  theme_classic() + xlim(-150,500) +  # NB: cuts off the long tails; throws an error ("Removed XXX rows containing missing values (stat_slabinterval)")
    scale_x_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500),
                     limits = c(-100,500),
                     labels = c("-100%", "0%", "100%", "200%", "300%","400%","500%")) +
  xlab("Contrast of posterior predicted probabilities") + 
  ylab("Density (normalized)") + ggtitle("How more likely are households to take ACT\nwhen subsidized by any amount?")

```

```{r pBplot-prep}
# Panel B: Contrast plot prep

# simulate counterfactual population: leave covariates as observed but toggle intervention on/off ofr all households
pB_pred <-  with(all_ill_prob_aggr,
                data.frame(
                  householdid = rep(householdid,4),
                  coartemprice = c(rep(40, length(householdid)), rep(60, length(householdid)),
                                   rep(100, length(householdid)), rep(500, length(householdid))),
                  B_head_age_bimps = rep(B_head_age_bimps,2),
                  trials = rep(trials,4),
                  totstrata = rep(totstrata,4)))

# plug posterior mean of imputations for missing age into prediction grid
age_impute <- rstan::extract(pBfit$fit,"Ymi_Bheadagebimps")$"Ymi_Bheadagebimps"
age_impute_mean <- apply(age_impute, 2, mean)
age_impute_idx <- which(is.na(pB_pred$B_head_age_bimps))
pB_pred[age_impute_idx,]$B_head_age_bimps <- age_impute_mean

# push posterior draws through prediction grid and calculate contrast
pB_marginal <- pB_pred |>
  tidybayes::add_epred_draws(pBfit,
                             re_formula = NULL, # include all random effects
                             resp = "tookact",
                             robust = FALSE) |> # posterior mean (FALSE) or median? 
  group_by(householdid, .draw) |>
  # get the percentage increase btw. subsidy levels vs. no subsidy
  mutate(contrast = c(((.epred[coartemprice==40]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      ((.epred[coartemprice==60]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      ((.epred[coartemprice==100]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      NA)) |> 
  ungroup()

```

```{r pBplot, include = TRUE, message=FALSE, fig.width=4.5, dependson = "pBplot-prep", fig.height=3, fig.cap = "\\label{pBplot} Results from \\texttt{pBfit} model. Contrast in predicted probabilities of taking an ACT between the price subsidy intervention (for each subsidy level) compared to no subsidy. Zero (the dotted line) represents equal chance of taking an ACT between the treatment and control groups. The densities are normalized and the gradients reflect posterior mass. The point represents the mode of the distribution with a 95% HPDI."}
# Panel B contrast plot: multiples
ggplot(pB_marginal[pB_marginal$coartemprice!=500,], 
       aes(y=as.factor(coartemprice), x = contrast)) +
  
  stat_halfeye(aes(fill = stat(x > 0), slab_alpha = stat(f)), 
               normalize="all",
               .width = 0.95,
               size = 1,
               point_interval = "mode_hdci",
               show.legend=FALSE, 
               n = 2000) +

  geom_vline(xintercept = 0, linetype = "dashed", alpha=0.75) +
  scale_fill_manual(values = c("black", "#3182BD")) +
  theme_classic()  +
  scale_y_discrete(labels = c("92%", "88%", "80%"), 
                   expand = c(0.1,0)) + # NB: cuts off the long tails; throws an error ("Removed XXX rows containing missing values (stat_slabinterval)")
  scale_x_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500),
                     limits = c(-100,500),
                     labels = c("-100%", "0%", "100%", "200%", "300%","400%","500%")) +
  xlab("Contrast of posterior predicted probabilities") + 
  ylab("ACT Subsidy Level") + ggtitle("How more likely are households to take ACT\nwhen subsidized by 80%, 88%, and 92%?")
```

The mode (black point) and 95% HPDI of the posterior predicted contrast between the treatment and the control group is thus `r round(tidybayes::mode_hdci(pA_marginal$contrast)$y, 2)`% [`r round(tidybayes::mode_hdci(pA_marginal$contrast)$ymin, 2)`, `r round(tidybayes::mode_hdci(pA_marginal$contrast)$ymax, 2)`], or roughly a doubling with the bulk of the posterior mass being above zero. This is a substantial effect given that the posterior predicted base rate of taking ACT in the control group is `r round(tidybayes::mode_hdci(pA_marginal[pA_marginal$act_any==0,]$.epred)$y, 3)*100`% [`r round(tidybayes::mode_hdci(pA_marginal[pA_marginal$act_any==0,]$.epred)$ymin, 3)*100`, `r round(tidybayes::mode_hdci(pA_marginal[pA_marginal$act_any==0,]$.epred)$ymax, 3)*100`].

Likewise, Figure \ref{pBplot} illustrates the computed contrast in posterior predicted probabilities across subsidy levels. The inference is very similar: there is roughly a doubling of chance of taking an ACT between the control and intervention groups, and the bulk of the posterior masses is above zero. Again, this is a substantial effect. While there is little difference between the three subsidy levels overall, perhaps unsurprisingly, the highest subsidy level (92%) has the highest posterior predicted change (`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==40,]$contrast)$y, 2)`% [`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==40,]$contrast)$ymin, 2)`, `r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==40,]$contrast)$ymax, 2)`]), with the effects of the 80% price subsidy (`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==100,]$contrast)$y, 2)`% [`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==100,]$contrast)$ymin, 2)`, `r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==100,]$contrast)$ymax, 2)`]) and the 88% price subsidy (`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==60,]$contrast)$y, 2)`% [`r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==60,]$contrast)$ymin, 2)`, `r round(tidybayes::mode_hdci(pB_marginal[pB_marginal$coartemprice==60,]$contrast)$ymax, 2)`]) being almost indistinguishable.

# Conclusion {#conclusion}
In conclusion, this re-analysis finds substantial evidence for the claim of the original study that *'... a very high subsidy ... increases access [to antimalarials]'* (p. 609.). Providing households with high price subsidies roughly doubles the chances of taking an ACT for an illness event with malaria-like symptoms, with a baseline likelihood of around `r round(tidybayes::mode_hdci(pA_marginal[pA_marginal$act_any==0,]$.epred)$y, 2)*100`%. This inference largely matches the original authors' findings, namely that '[s]ubsidies of 80 percent or more increase the likelihood that an illness is treated with an ACT by 16-23 percentage points (an 85-118 percent increase) [...]' (p. 628). 

With that said, the present re-analysis yields a large degree of uncertainty in inference. This is at least partly due to the fact that the re-analysis marginalizes over the distribution of covariates. Excluding the random effects of strata (i.e., getting predictions for an average stratum and ignoring stratum-specific variance) reduces the uncertainty such that all 95% intervals no longer (or only barely) include zero (i.e., a 'statistically significant' difference; see Figures \ref{pAplot-cond} and \ref{pBplot-cond}).

Note, finally, that given the overlap between the presently obtained results and those of the original study (and also due to time and timing), I did not attempt to replicate any follow-up analyses reported in the original study, such as the ones reported in their Panel A and B, Figure 4, where the self-reported data were cross-checked with observational and behavioral data. For the same reasons, I also did not attempt to replicate their baseline summary statistics (their Table 1). A reasonable balance between control and treatment groups is essential for the assumption of conditional exchangeability that underlies our average treatment effect estimates.

\newpage

# Supplementary plots {#supps}

```{r pAplot-cond, include = TRUE, message=FALSE, fig.width=4.5, fig.height=3, fig.cap = "\\label{pAplot-cond} Same as Figure \\ref{pAplot}, but ignoring strata-specific random effects."}
# Panel A: Contrast plot prep (excluding random effects)
pA_conditional <- pA_pred |>
  tidybayes::add_epred_draws(pAfit, 
                             re_formula = NA, # exclude random effects
                             resp = "tookact",
                             robust = FALSE) |>
  group_by(householdid, .draw) |>
  mutate(contrast = ((.epred[act_any==1]-.epred[act_any==0])/.epred[act_any==0])*100) |> 
  ungroup()

# Panel A contrast plot (excluding random effects)
ggplot(pA_conditional, aes(x = contrast)) +

  stat_halfeye(aes(fill = stat(x > 0), slab_alpha = stat(f)), 
               normalize="all",
               .width = 0.95,
               size = 1,
               point_interval = "mode_hdci",
               show.legend=FALSE) +
  
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("black", "#3182BD")) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha= 0.5) +
  theme_classic() + xlim(-150,500) + 
    scale_x_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500),
                     limits = c(-100,500),
                     labels = c("-100%", "0%", "100%", "200%", "300%","400%","500%")) +
  xlab("Contrast of posterior predicted probabilities") + 
  ylab("Density (normalized)") + ggtitle("How more likely are households to take ACT\nwhen subsidized by any amount?",
                                      subtitle = "Ignoring strata-specific random effects.")

```


```{r pBplot-cond, include = TRUE, message=FALSE, fig.width=4.5, fig.height=3, fig.cap = "\\label{pBplot-cond} Same as Figure \\ref{pBplot}, but ignoring strata-specific random effects."}
# Panel B: Contrast plot prep (excluding random effects)
pB_conditional <- pB_pred |>
  tidybayes::add_epred_draws(pBfit,
                             re_formula = NA, # exclude random effects
                             resp = "tookact",
                             robust = FALSE) |>
  group_by(householdid, .draw) |>
  mutate(contrast = c(((.epred[coartemprice==40]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      ((.epred[coartemprice==60]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      ((.epred[coartemprice==100]-.epred[coartemprice==500])/.epred[coartemprice==500])*100,
                      NA)) |> 
  ungroup()

# Panel B contrast plot (excluding random effects)
ggplot(pB_conditional[pB_conditional$coartemprice!=500,], 
       aes(y=as.factor(coartemprice), x = contrast)) +
  
  stat_halfeye(aes(fill = stat(x > 0), slab_alpha = stat(f)), 
               normalize="all",
               .width = 0.95,
               size = 1,
               point_interval = "mode_hdci",
               show.legend=FALSE) +

  geom_vline(xintercept = 0, linetype = "dashed", alpha=0.75) +
  scale_fill_manual(values = c("black", "#3182BD")) +
  theme_classic()  +
  scale_y_discrete(labels = c("92%", "88%", "80%"), 
                   expand = c(0.1,0)) +
  scale_x_continuous(breaks = c(-100, 0, 100, 200, 300, 400, 500),
                     limits = c(-100,500),
                     labels = c("-100%", "0%", "100%", "200%", "300%","400%","500%")) +
  xlab("Contrast of posterior predicted probabilities") + 
  ylab("ACT Subsidy Level") + ggtitle("How more likely are households to take ACT\nwhen subsidized by 80%, 88%, and 92%?",
                                      subtitle = "Ignoring strata-specific random effects.")
```

\newpage

# R packages and dependencies {#pkgs}

```{r cite-package, include=TRUE, results = 'asis'}
grateful::cite_packages(dependencies = TRUE, cite.tidyverse = TRUE, output = "paragraph")
```

```{r save-data}
save.image("multi100_fits.Rdata")
```

\newpage

# References {-}

<div id="refs"></div>

